Robust calibration of numerical models based on relative regret

### 2019-12-19 article.tex
hat notation, biblio update

%% main text
\section*{Introduction}
\label{}

@@

Accounting for the probabilistic nature of  $\mathbf{U}$ leads to study the distribution of the random variable $J(\mathbf{k},\mathbf{U})$, or the distribution of its minimisers ${\mathbf{k}}_{\mathbf{U}}$. The latter is referred as 
the distribution of the conditional minimisers, notion that appeared notably in~\cite{villemonteix_informational_2006} and in~\cite{hennig_entropy_2011} for a global optimisation purpose. Both approaches and related robust estimates are described in Section~\ref{robust formulations}. Section~\ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems.  The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$. Illustration of the various described methods are given on a numerical exemple in Section~\ref{sec:SWE_application}.

@@

% ----------------------------------------------------------------------------
\subsection{Most probable estimate}
Let us consider the minimal cost attainable in each configuration brought by $\mathbf{u}$.
The resulting conditional minimum is denoted $J^*$:
\begin{equation}
\label{eq:def_Jstar}
J^*: \mathbf{u} \in\Uspace \longmapsto J^*(\mathbf{u}) = \min_{\mathbf{k}\in \Kspace} J(\mathbf{k},\mathbf{U}=\mathbf{u})
\end{equation}
Similarly, the function of conditional minimisers can then defined by:
  \begin{equation}
  \label{eq:conditional_minimiser}
   \mathbf{k}^*: \mathbf{u}\in\Uspace \longmapsto \mathbf{k}^*(\mathbf{u}) = \mathbf{k}_{\mathbf{u}}=  \argmin_{{\mathbf{k}}\in\Kspace} J({\mathbf{k}},\mathbf{U}=\mathbf{u})
  \end{equation}
Using this function, we can define the corresponding random variable $\mathbf{K}^*$ as
  \begin{equation}
    \label{eq:def_study_minimisers}
    \mathbf{K}^*= \mathbf{k}^*(\mathbf{U}),
  \end{equation}
and its associated density function $p_{\mathbf{K}^*}(\mathbf{k})$, that will be further referred as the density of minimisers.
The mode of this density is called the Most Probable Estimate (MPE) and is noted  $\kmpe$:
\begin{equation}
  \label{eq:MPE}
  \kmpe = \argmax_{\mathbf{k} \in\Kspace} p_{\mathbf{K}^*}(\mathbf{k}) 
\end{equation}
To give some intuition on this estimate, let us imagine that the distribution of minimisers is a dirac centered on $\kmpe$. Then it would mean that this estimate is the minimiser of the cost function whatever the realisation of the uncertain variable, therefore optimal in all conditions. 
If the distribution $p_{\mathbf{K}^*}$ is heavily dominated by a single value, the MPE may be a good candidate for robust control. This is not so obvious in case of a multimodal distribution.

In general, an analytical form of $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an estimation $\hat{p}_{\mathbf{K}^*}$ must be used, and its maximum computed to get the MPE.
Once again, a set of samples  $\{\mathbf{u}^i\}_{i=1\dots N}$ can be used to compute the set $\{\mathbf{k}_{\mathbf{u}^i}\}_{i=1\dots N}$, from which one can 
approximate  $p_{\mathbf{K}^*}$. The resulting approximation and therefore its mode, is sensitive to the density estimation method. Main methods are KDE  (Kernel Density Estimation)~\cite{elise}, and  EM (Expectation-Maximisation)~\citep{dempster_maximum_1977}.

@@

Our approach is based on the will to be as close as possible to the conditional minimiser, with high probability. At a level $p$, in addition to the estimation, we have the relaxation coefficient $\alpha_p$ that bounds with probability $p$ the relative error of the cost function, that helps us assess the conservativeness of the proposed estimation.

@@

Practically speaking, the estimation of those quantities is very crude, so the computational cost may be very expensive. As perspective, specific strategies have to be created, based for instance on sequential design of computer experiments using Gaussian processes, to diminish the amount of runs needed of the numerical model.. Ideally, one would want to develop a acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.
Finally, the models upon which this calibration procedure have been applied are very simplistic. We plan in the future to apply this to the robust calibration of the bottom friction of a realistic model of the ocean.
% \victor{À faire à la fin}
% This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.

@@

\bibliographystyle{elsarticle-num-names} 
\bibliography{bibzotero}

>>>>

%% main text
\section*{Introduction}
\label{sec:intro}

@@

Accounting for the probabilistic nature of  $\mathbf{U}$ leads to study the distribution of the random variable $J(\mathbf{k},\mathbf{U})$, or the distribution of its minimisers ${\mathbf{k}}_{\mathbf{U}}$. The latter is referred as 
the distribution of the conditional minimisers, notion that appeared notably in~\cite{villemonteix_informational_2006} and in~\cite{hennig_entropy_2011} for a global optimisation purpose. Both approaches and related robust estimates are described in Section~\ref{robust formulations}. Section~\ref{sec:relax_constraint} introduces a new class of estimators, by relaxing the constraint of optimality and defining regions of acceptability, similarly as~\cite{buhmann_robust_2013} in discrete combinatorial problems, or~\cite{kouvelis_algorithms_1992,snyder_stochastic_2004} in operation research. The intention is that a robust estimate provides values of the cost function close enough to the attainable minimum for each configuration induced by $\mathbf{u}\in\Uspace$. Illustration of the various described methods are given on a numerical exemple in Section~\ref{sec:SWE_application}.

@@

% ----------------------------------------------------------------------------
\subsection{Most probable estimate}
Let us consider the minimal cost attainable in each configuration brought by $\mathbf{u}$.
The resulting conditional minimum is denoted $J^*$:
\begin{equation}
\label{eq:def_Jstar}
J^*: \mathbf{u} \in\Uspace \longmapsto J^*(\mathbf{u}) = \min_{\mathbf{k}\in \Kspace} J(\mathbf{k},\mathbf{U}=\mathbf{u})
\end{equation}
Similarly, the function of conditional minimisers can then defined by:
  \begin{equation}
  \label{eq:conditional_minimiser}
   \mathbf{k}^*: \mathbf{u}\in\Uspace \longmapsto \mathbf{k}^*(\mathbf{u}) = \mathbf{k}_{\mathbf{u}}=  \argmin_{{\mathbf{k}}\in\Kspace} J({\mathbf{k}},\mathbf{U}=\mathbf{u})
  \end{equation}
Using this function, we can define the corresponding random variable $\mathbf{K}^*$ as
  \begin{equation}
    \label{eq:def_study_minimisers}
    \mathbf{K}^*= \mathbf{k}^*(\mathbf{U}),
  \end{equation}
and its associated density function $p_{\mathbf{K}^*}(\mathbf{k})$, that will be further referred as the density of minimisers.
The mode of this density is called the Most Probable Estimate (MPE) and is noted  $\kmpe$:
\begin{equation}
  \label{eq:MPE}
  \kmpe = \argmax_{\mathbf{k} \in\Kspace} p_{\mathbf{K}^*}(\mathbf{k}) 
\end{equation}
To give some intuition on this estimate, let us imagine that the distribution of minimisers is a dirac centered on $\kmpe$. Then it would mean that this estimate is the minimiser of the cost function whatever the realisation of the uncertain variable, therefore optimal in all conditions. 
If the distribution $p_{\mathbf{K}^*}$ is heavily dominated by a single value, the MPE may be a good candidate for robust control. This is not so obvious in the case of a multimodal distribution.

In general, an analytical form of $p_{\mathbf{K}^*}$ is usually impossible to obtain, so an estimation $\hat{p}_{\mathbf{K}^*}$ must be used, and its maximum computed to get the MPE.
In the rest of the paper, the hat notation will indicate an estimation using numerical values of the underlying theoretical quantity.
Once again, a set of samples  $\{\mathbf{u}^i\}_{i=1\dots N}$ can be used to compute the set $\{\mathbf{k}_{\mathbf{u}^i}\}_{i=1\dots N}$, from which one can 
approximate  $p_{\mathbf{K}^*}$. The resulting approximation and therefore its mode, is sensitive to the density estimation method. Main methods are KDE  (Kernel Density Estimation)~\cite{elise}, and EM (Expectation-Maximisation)~\citep{dempster_maximum_1977}.

@@

Our approach is based on the will to be as close as possible to the conditional minimisers with high probability. At a level $p$, in addition to the estimation, we have the relaxation coefficient $\alpha_p$ that bounds with probability $p$ the relative error of the cost function, that helps us assess the conservativeness of the proposed estimation.

@@

Practically speaking, the estimation of those quantities is very crude, so the computational cost may be very expensive. As perspective, specific strategies have to be created, based for instance on sequential design of computer experiments using Gaussian processes, to diminish the amount of runs needed of the numerical model. Ideally, one would want to develop a acquisition criterion, that makes the balance between the minimisation of a well-chosen probability of failure, and the exploration around the conditional minimisers.
Finally, the models upon which this calibration procedure have been applied are very simplistic. We plan in the future to apply this to the robust calibration of the bottom friction of a realistic model of the ocean.
% \victor{À faire à la fin}
% This paper deals with the problem of robust calibration of a computer code in the presence of uncertain inputs.

@@

\bibliographystyle{elsarticle-num-names} 
\bibliography{biblio_file}
